---
output: github_document
references:
- id: lanera18
  title: Building Comprehensive Searches including PubMed and ClinicalTrials.gov Through a Machine Learning Approach for Systematic Reviews
  author:
  - family: Lanera
    given: Corrado
  - family: Minto
    given: Clara
  - family: Sharma
    given: Abhinav
  - family: Gregori
    given: Dario
  - family: Berchialla
    given: Paola
  - family: Baldi
    given: Ileana
  container-title: Submitted
  publisher: Under revision
  type: article-journal
  issued:
    year: 2018
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.org/UBESP-DCTV/costumer.svg?branch=master)](https://travis-ci.org/UBESP-DCTV/costumer)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/UBESP-DCTV/costumer?branch=master&svg=true)](https://ci.appveyor.com/project/UBESP-DCTV/costumer)
[![Coverage status](https://codecov.io/gh/UBESP-DCTV/costumer/branch/master/graph/badge.svg)](https://codecov.io/github/UBESP-DCTV/costumer?branch=master)

# costumer

The goal of costumer is to provide the data, the functions, scripts for the
analyses and the documentation (report) within the relative templates for
the paper *Building Comprehensive Searches including PubMed and
ClinicalTrials.gov Through a Machine Learning Approach for Systematic
Reviews*.

## Installation

<!-- You can install the released version of costumer from -->
<!-- [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("costumer") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/)
with the following procedure:

```{r, eval = FALSE}
## If you do not have the `devtools` package installed, please install it
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/costumer")
```


## folders' organization

* `R/` contains all the functions provided to implement the analyses
* `tests/` contains all the automated test to run for CI
* `man/` contains the documents for each function or data provided
  (accessible in R by `?<name_of_the_object>`)
* `data-raw/` contains all the script used to import and manage the data used
  in the analyses and in the (automated) tests of the package
* `data/` contains the data provided by the package. In particoular, it
  contains:
    - the customized `caret` models (used to incorporate a correct 
      management of cross-validation process with textual data, especially
      for iDF reweighting) --- `*_cvAble.rda`;
    - the customized functions for the unbalance management ---
      `R[OU]S(3565|5050)_new.rda`;
    - sample data used in the automated tests --- `liu_*.rda`.
* `inst/` contains two folders:
    - `analyses/` which contains the script used to perform all the analyses 
      reported in @lanera18;
    - `doc/` which contains the data-dictionary for the original
      clinicaltrial.gov data

> **Note**: the main data used are to huge to be included in a R package or
>  in a github repository.
>  [Here](https://1drv.ms/f/s!AtlSkmthbrG4i8lA1fk5LPhmsOt0pg) you can find a
>  folder named `non_git_nor_build_derived_data/` (2.86 GB) which contains:
>
>  - `171106-all_svm_3565/` folder with all the outputs of the last
>     analyses:
>      + `CV-Plots/` folder which contains all the cross-validation plots
>        representing the decision levels for the tuning parameter used in
>        each model;
>      + `models/` folder which contains all the trained models;
>      + `hutch3.rda` data which contains the `hutch3` data frame containing
>        all the data-step of the analyses, i.e. starting data, preprocessed
>        data, dmt, testing, data, model used, plots provided, ...
>        everything!
>      + `*.txt` log files.
>  - `raw_pubmed/` folder with the data used to train the models, which are
>    needed to run the script `data-raw/import_pubmed.R`. Hence, if you 
>    would like to run that script by yourself you need to put this folder
>    as it is into the `data-raw/` one.
>  - `raw_ctgov.zip` zip file with the data used to test the models, i.e.,
>    the clinicaltrial.gov snapshot used and which is (when unzipped)
>    needed to run the script `data-raw/import_ctgov.R`.  Hence, if you 
>    would like to run that script by yourself you need to unzip this file
>    and put the output folder as it is (~841 MB) into the `data-raw/` one.
>  - `random4h28.xlsx` file with the sample data used to (automated) test
>    functions provided with the package, which is needed to run the script
>    `data-raw/import_liu.R`.  Hence, if you would like to run that script
>    by yourself you need to put this file as it is into the `data-raw/`
>    folder.
>  - `summaries_*.rda` the outputs ready-to-use of the functions
>    `import_*.R` which are needed to run the script of the analyses. Hence,
>    if you would like to run that script by yourself you need to put this
>    files as they are into the `data/` folder.
>  - `test_*.rda` data which are the outputs of the function
>     `data-raw/ct_corpus_and_dtm.R` which are also needed (and here are
>     ready-to-use) to run the script of the analyses. Hence, if you would
>     like to run that script by yourself you need to put this files as they
>     are into the `data/` folder.


## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example)
to <https//github.com/UBESP-DCTV-imthcm/issues>

## Reference
